Hippocampal segmentation with MAGeT

### 2012-12-07 paper.Rnw
Further work on methods section

\SweaveOpts{echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', tidy = FALSE, comment = NA, cache = TRUE}
<<loadpackages, results="hide", echo=FALSE, cache=FALSE>>=
library(ggplot2)
library(Hmisc)
library(reshape2)
library(ADNIMERGE)
library(plyr)
options(digits=3)
theme_set(theme_bw())
@

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{algorithm, color, algpseudocode, amsmath, url, geometry, ctable }
\usepackage[square,numbers]{natbib}
\setlength{\marginparwidth}{1.2in}
\newcommand{\marginnote}[1]{\-\marginpar[\raggedleft\footnotesize #1]{\raggedright\footnotesize #1}}
\newcommand{\todo}[1]{\begin{kframe}{\textcolor{red}{TODO #1}}\end{kframe}}
\newcommand{\mc}[1]{\todo{(MC) #1}}

%{\marginpar{ \textcolor{red}{\\ TODO: #1 \\} }
\begin{document}

@@

\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%                               METHODS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}

@@

\todo{Note that algorithm does not specify a registration algorithm or fusion 
method\citep{Chakravarty2012}.  Performance on these is test in experiments}

@@

\subsubsection{ADNI-1 1.5T Screening}
\todo{- image characteristics}
\todo{- describe SNT manual segmentations}
\todo{- baseline/cross-validation dataset demographics?}

<<ADNI-1-screening-demographics, echo=F, results="asis",cache=FALSE>>=
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 + MMSE, 
               data = adnimerge, subset = VISCODE == 'bl',   
               method = "reverse", test=FALSE, overall=TRUE)

latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=TRUE,
      caption="ADNI-1 1.5T Screening demographics")
@
\todo{Check table only includes 1.5T from the Screening}

\subsubsection{SZ First Episode Patients}
\todo{image characteristics, demographics}
<<FEP-SZ-demographics, echo=F, results="asis",cache=FALSE>>=
fep_sz_demographics = read.csv("data/SZ_demographics.csv", na.strings=c("","."))
fep_sz_demographics = subset(fep_sz_demographics, Anon <= 81)
tab <- summary(DX ~ Age + Gender + Handedness + Education + SES + FSIQ,
               data=fep_sz_demographics, method = "reverse", test = FALSE)
latex(tab, file="", size="scriptsize", 
      caption="Schizophrenia First Episode Patient Demographics")
@

@@

\todo{link to MNI website here}
\todo{command line}

@@

We used the following command line when running the ANTS command, 
\begin{verbatim}
  mincANTS 3 -m PR[target_file.mnc,source_file.mnc,1,4] 
   --number-of-affine-iterations 10000x10000x10000x10000x10000 
   --affine-gradient-descent-option 0.5x0.95x1.e-4x1.e-4
   --use-Histogram-Matching --MI-option 32x16000
   -r Gauss[3,0] -t SyN[0.5] -i 100x100x100x20
   -o transformation.xfm
 \end{verbatim}
These settings were adapted from the "reasonable starting point" given in the
ANTS manual. \todo{reference manual?}

@@

This method is similar to cross-correlation weighted voting 
except that image similarity is calculated by the normalised 
mutual information score over the region of interest. \todo{reference?}

@@

Each segmentation was evaluated against the 'gold-standard' manual segmentation
from the dataset using the Dice Kappa ($\kappa$) overlap metric:

@@

where $a$ is the number of voxels common to the candidate segmentation and the
gold standard and $b+c$ is the sum of the voxels uniquely identified by either
the automatically generated candidate segmentation or the gold-standard.
\todo{I would do this after you define the experiments}

%%%%%                            Experiments                               %%%%%

\subsection{Experiments}

@@

{\bf Dataset evaluated.} 69 1.5T images were randomly selected from the 
{\em ADNI1:Screening 1.5T} standardized dataset.  Demographics for this subset 
are shown in Table X\todo{FIXME: table reference}.

<<ADNI-69-demographics, echo=F, results="asis",cache=FALSE>>=
adni_69_RIDs = c("295","413","619","685","729","782","938","954",
                 "1018","1155","907","981","222","324","448","546",
                 "553","572","602","610","814","1341","675","681",
                 "731","1130","41","68","70","101","249","293","316",
                 "414","698","1206","1222","1339","751","1030","3",
                 "5","10","16","22","53","168","183","241","1205",
                 "328","1095","991","213","159","337","343","642",
                 "753","1109","1217","29","56","1188","1293","149",
                 "382","431","1202")
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 + MMSE, 
               data = adnimerge, subset = VISCODE == 'bl' & RID %in% adni_69_RIDs, 
               method = "reverse", test=FALSE, overall=TRUE)

latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=TRUE,
      caption="ADNI-1 cross-validation subset demographics")
@

@@

{\bf Registration method.}  Both the ANTS and ANIMAL registration methods were 
used.
\todo{In ANIMAL, images aligned to TAL space}

@@

\todo{ number of registrations/comparisions }

@@

{\bf Registration method.}  - ANTS as it performed best in the cross-validation
experiment. \todo{how to reference results whilst still in Methods?}

@@

Since hippocampal segmentation protocols differ between the ADNI labels and
Winterburn atlases, this poses a problem for direct similarity comparisons
between labels produced by MAGeT brain and the ADNI labels.  \todo{explain why
we did(n't) resegment the ADNI images with a the low-res protocol.}

@@

Additionally, we compared classification accuracy of subjects
by diagnosis based on hippocampal volume using both the SMT labels and our
produced labels.  \todo{description of validation -- rms {\tt validate} or
t-test: contrast with QDA or LDA (Coupe 2011) used in LOOCV}

%%%%%
%%%%%          Experiments: SZ First Episode Patient Validation           %%%%%
%%%%%
\subsubsection{SZ First Episode Patient Validation}
 To validate that MAGeT's performance generalises to other diseases.
Measure performance using best parameter settings on a different disease dataset.

{\bf Dataset evaluated.} SZ First Episode Patients

{\bf Atlas and template libary.} two different atlas sets: a manual hippocampal
segmentation of patients, and Winterburn atlas set.

@@

%%%%%
%%%%%              Experiments: Winterburn Atlases Validation              %%%%%
%%%%%
\subsubsection{Winterburn Atlases Validation}
{\bf Dataset evaluated.} T1 BRAVO scans of the same subjects included in the 
Winterburn atlas set.  These scans are taken within .... weeks of the scans for 
the Winterburn atlases.

{\bf Atlas and template libary.} Atlas library is Winterburn T1 atlases.  
Template library consists of all five T1 BRAVOs, plus 15 T1 healthy control images.

@@

{\bf Evaluation.}  Leave one out cross-validation (LOOCV) in which all five
subjects are segmented in separate runs of MAGeT brain.  In each run, the subject
to be segmented is excluded from the Atlas library (so only four atlases are used).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%                               Results
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}

%%%%%
%%%%%                  Results: ADNI-1 cross-validationn                   %%%%%
%%%%%
\subsubsection{ADNI-1 Cross-Validation}

 - find significant improvement over multi-atlas performed with the same
  parameters. Also, find smoothed performance is monotonically increasing but asymptotic
  in size of both template and atlas library, with peak performance reached after 15
  templates. \todo{Can we statistically capture "peak" performance?  The point at which 
  gains become statistically insignificant?}

@@

Multi-atlas means:

<<a2a_multiatlas_means, results="asis",cache=FALSE>>=
latex(merge(a_ma_means, t_ma_means, by="num_atlases"), colheads=c("Atlases", "ANTS", "ANIMAL"), file="", dec=2)
@
\begin{table}
    \begin{tabular}{c|c|c}
        Number of Atlases & ANIMAL Kappa (Jaccard) & ANTS Kappa (Jaccard) \\ \hline
        3                 & 0.76 (0.63)             & 0.80 (0.69)          \\ 
        4                 & 0.75 (0.62)             & 0.79 (0.67)          \\ 
        5                 & 0.79 (0.66)             & 0.82 (0.71)          \\ 
        6                 & 0.78 (0.65)             & 0.82 (0.70)          \\ 
        7                 & 0.80 (0.67)             & 0.83 (0.72)          \\ 
        8                 & 0.79 (0.67)             & 0.83 (0.72)          \\ 
        9                 & 0.80 (0.68)             & 0.84 (0.73)          \\
    \end{tabular}
\end{table}

- more atlases -> better performance
- larger template library -> better performance, but tails off around 10-15 templates
- no significant difference between majority or weighted vote methods (haven???t tested this statistically though). 
- consistently performs better than average naive performance by XXX
- using ANTS, with a large enough template library (>12) MAGeT brain performs
  better than the average multi-atlas approach with the same number of atlases.
  using ANIMAL, 5 or more atlases needed before boost seen. 
- more atlases -> smaller template library required to improve on average multi-atlas performance
- discuss variance?  best/worst case? --how often do we expect random template library selection to work decently

\todo{cost (in registrations) / benefit trade off graph:  show number of registrations per Kappa?  or hours of manual labour per Kappa?)}

\subsubsection{Winterburn Atlas Segmentation of ADNI Baseline Images}

- A2A shows that if atlas population strongly(?) represents subject set
  variability, then free choice from atlas population will produce improvements
(we know this b/c of extensive validation trials). 
- what about in the case where atlas population doesn???t strongly represent
  subject set variability (e.g. a priori atlas set)?  then, we can use atlas
selection to refine atlas set?

\todo{Kappa against our manual rater is low}

@@

# recode VISCODE

viscode_levels = list("bl"=1,"bl"=2, "m06"=3,"m12"=4)
yr1$VISCODE <- as.factor(yr1$Visit)
levels(yr1$VISCODE) <-viscode_levels

@@

attach(combined)
vols = data.frame(RID = RID, VISCODE = VISCODE, DX = DX.bl,
                  MAGeT = MAGeT_L + MAGeT_R, 
                  MAPER = MAPER_L + MAPER_R, 
                  SNT   = SNT_L + SNT_R, 
                  UCSD  = UCSD_L + UCSD_R,
                  FS    = FS_L + FS_R, 
                  FSL   = FSL_L + FSL_R)
write.csv(vols, "data/ADNI_baseline_volumes_combined_volumes.csv")
@

\begin{figure}[h]
<<ADNI-baseline-volumes-boxplot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-prep',cache=T>>=
totals = read.csv("data/ADNI_baseline_volumes_combined_volumes.csv")
qplot(DX,value,data=melt(totals,measure.vars=c("FS", "FSL","UCSD", "MAPER","MAGeT","SNT"),na.rm=T),
      colour=variable,geom="boxplot") + 
        xlab("Diagnosis") + ylab("Total Hippocampal Volume (mm3)")

@@

\subsubsection{First Episode Schizophrenic patients}
High volume correlation between Winterburn segmentation volumes and ground truth.  (High-ish?) Kappa when using manual segmentations as Atlases.

@@

@
  \caption{{\bf First Episode Schizophrenic Patients.} Comparison of total HC volumes for MAGeT against manually rated volumes of}
  \label{SZ_volumes}
\end{figure}

Some other text here... 
\end{document}

>>>>

\SweaveOpts{echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', tidy = FALSE, comment = NA, cache = TRUE}

<<loadpackages, results="hide", echo=FALSE, cache=FALSE>>=
library(ggplot2)
library(Hmisc)
library(reshape2)
library(ADNIMERGE)
library(plyr)
options(digits=3)
theme_set(theme_bw())
@

\documentclass[twocolumn]{article}
\usepackage[margin=1in]{geometry}
\usepackage{algorithm, color, algpseudocode, amsmath, url, geometry, ctable }
\usepackage[square,numbers]{natbib}
\setlength{\marginparwidth}{1.2in}
\newcommand{\marginnote}[1]{\-\marginpar[\raggedleft\footnotesize #1]{\raggedright\footnotesize #1}}
\newcommand{\comment}[1]{\begin{kframe}{\textcolor{red}{#1}}\end{kframe}}
\newcommand{\todo}[1]{\comment{TODO #1}}
\newcommand{\mc}[1]{\comment{MC: #1}}
\begin{document}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               METHODS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}

@@

\todo{Note that our algorithm does not specify a registration algorithm or
fusion method\citep{Chakravarty2012}.  Performance on options is tested in our
experiments}

@@

\subsubsection{ADNI-1 1.5T Screening}
\todo{include image characteristics}
\todo{describe SNT manual segmentations}

\begin{figure*}
<<ADNI-1-screening-demographics, echo=F, results="asis",cache=FALSE>>=
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 + MMSE, 
               data = adnimerge, subset = VISCODE == 'bl',   
               method = "reverse", test=FALSE, overall=TRUE)

latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=TRUE,
      caption="ADNI-1 1.5T Screening demographics")
@
\end{figure*}

\todo{Check demographics table only includes 1.5T from the Screening}

\subsubsection{SZ First Episode Patients}
\todo{include image characteristics}
\begin{figure*}
<<FEP-SZ-demographics, echo=F, results="asis",cache=FALSE>>=
fep_sz_demographics = read.csv("data/SZ_demographics.csv", na.strings=c("","."))
fep_sz_demographics = subset(fep_sz_demographics, Anon <= 81)
tab <- summary(DX ~ Age + Gender + Handedness + Education + SES + FSIQ,
               data=fep_sz_demographics, method = "reverse", test = FALSE)
latex(tab, file="", size="scriptsize", 
      caption="Schizophrenia First Episode Patient Demographics")
@
\end{figure*}

@@

\todo{link to MNI website here}
\todo{show command line used}

@@

We used the following command line when running the ANTS command, 
\begin{verbatim}
  mincANTS 3 -m PR[target_file.mnc,source_file.mnc,1,4] 
   --number-of-affine-iterations 10000x10000x10000x10000x10000 
   --affine-gradient-descent-option 0.5x0.95x1.e-4x1.e-4
   --use-Histogram-Matching --MI-option 32x16000
   -r Gauss[3,0] -t SyN[0.5] -i 100x100x100x20
   -o transformation.xfm
 \end{verbatim}
These settings were adapted from the "reasonable starting point" given in the
ANTS manual. \todo{include a reference to manual?}

@@

This method is similar to cross-correlation weighted voting 
except that image similarity is calculated by the normalised 
mutual information score over the region of interest. 
\todo{is there a reference for NMI voting?}

@@

Two segmentation can be compared using the Dice Kappa ($\kappa$) overlap metric:

@@

where $a$ is the number of voxels common to both segmentations and $b+c$ is the
sum of the voxels uniquely identified by either segmentation.  Using this metric
we can compare an automatically generated segmentation to a gold-standard
segmentation.

%%%%%
%%%%%                            Experiments                               %%%%%
%%%%%
\subsection{Experiments}

@@

{\bf Dataset evaluated.} 69 1.5T images were randomly selected from the 
{\em ADNI1:Screening 1.5T} standardized dataset.  Demographics for this subset 
are shown in Table X
\todo{FIXME: table reference}.

\begin{table*}
<<ADNI-69-demographics, echo=F, results="asis",cache=FALSE>>=
adni_69_RIDs = c("295","413","619","685","729","782","938","954",
                 "1018","1155","907","981","222","324","448","546",
                 "553","572","602","610","814","1341","675","681",
                 "731","1130","41","68","70","101","249","293","316",
                 "414","698","1206","1222","1339","751","1030","3",
                 "5","10","16","22","53","168","183","241","1205",
                 "328","1095","991","213","159","337","343","642",
                 "753","1109","1217","29","56","1188","1293","149",
                 "382","431","1202")
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 + MMSE, 
               data = adnimerge, subset = VISCODE == 'bl' & RID %in% adni_69_RIDs, 
               method = "reverse", test=FALSE, overall=TRUE)

latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=TRUE,
      caption="ADNI-1 cross-validation subset demographics")
@
\end{table*}

@@

{\bf Registration method.}  Both the ANTS and ANIMAL registration methods were
used.

\todo{In ANIMAL, images aligned to TAL space}

@@

\todo{ show off the number of registrations/comparisions we did}

@@

{\bf Registration method.} ANTS, as it performed best in the cross-validation
experiment.

\todo{Is it okay to reference results whilst still in Methods?}

@@

Since hippocampal segmentation protocols differ between the ADNI labels and
Winterburn atlases, this poses a problem for direct similarity comparisons
between labels produced by MAGeT brain and the ADNI labels.

\todo{explain why we did(n't) resegment the ADNI images with the low-res
protocol and compare directly like that.}

@@

Additionally, we compared classification accuracy of subjects
by diagnosis based on hippocampal volume using both the SMT labels and our
produced labels.

\todo{Include a description of validation process.. Note that we could use rms
{\tt validate} or t-test: contrast with QDA or LDA (Coupe 2011) used in LOOCV,
with adni/our segmentations}

%%%%%
%%%%%          Experiments: SZ First Episode Patient Validation           %%%%%
%%%%%
\subsubsection{SZ First Episode Patient Validation}

{\bf Dataset evaluated.} To validate that MAGeT performance generalises to other
diseases, we measure the performance using the best parameter settings previous
found, on a dataset consiting of first episode schizophrenia patients.
\todo{Refer to the FEP description above... or just include it here}.

{\bf Atlas and template libary.} - two different atlas sets: a manual
hippocampal segmentation of patients, and Winterburn atlas set.

@@

%%%%%
%%%%%              Experiments: Winterburn Atlases Validation              %%%%%
%%%%%
\subsubsection{Winterburn Atlases Validation}
{\bf Dataset evaluated.} - T1 BRAVO scans of the same subjects included in the 
Winterburn atlas set.  These scans are taken within .... weeks of the scans for 
the Winterburn atlases.

{\bf Atlas and template libary.} - Atlas library is Winterburn T1 atlases.  
Template library consists of all five T1 BRAVOs, plus 15 T1 healthy control images.

@@

{\bf Evaluation.}  - Leave one out cross-validation (LOOCV) in which all five
subjects are segmented in separate runs of MAGeT brain.  In each run, the subject
to be segmented is excluded from the Atlas library (so only four atlases are used).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               Results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

%%%%%
%%%%%                  Results: ADNI-1 cross-validationn                   %%%%%
%%%%%
\subsection{ADNI-1 Cross-Validation}

- find significant improvement over multi-atlas performed with the same
  parameters. Also, find smoothed performance is monotonically increasing but
  asymptotic in size of both template and atlas library, with peak performance
  reached after 15 templates.

\todo{Can we statistically capture what "peak" performance is?  Something like,
the point at which gains become statistically insignificant?}

@@

<<a2a_multiatlas_means, results="asis",cache=FALSE>>=
latex(merge(a_ma_means, t_ma_means, by="num_atlases"),
colheads=c("Atlases", "ANTS", "ANIMAL"), file="", dec=2,
	caption="Multi-atlas means")
@

%\begin{table}
%    \begin{tabular}{c|c|c}
%        Number of Atlases & ANIMAL Kappa (Jaccard) & ANTS Kappa (Jaccard) \\ \hline
%        3                 & 0.76 (0.63)             & 0.80 (0.69)          \\ 
%        4                 & 0.75 (0.62)             & 0.79 (0.67)          \\ 
%        5                 & 0.79 (0.66)             & 0.82 (0.71)          \\ 
%        6                 & 0.78 (0.65)             & 0.82 (0.70)          \\ 
%        7                 & 0.80 (0.67)             & 0.83 (0.72)          \\ 
%        8                 & 0.79 (0.67)             & 0.83 (0.72)          \\ 
%        9                 & 0.80 (0.68)             & 0.84 (0.73)          \\
%    \end{tabular}
%\end{table}

Ideas:
\begin{itemize}
\item more atlases -> better performance
\item  larger template library -> better performance, but tails off around 10-15 templates
\item  no significant difference between majority or weighted vote methods (haven???t tested this statistically though). 
\item  consistently performs better than average naive performance by XXX
\item  using ANTS, with a large enough template library (>12) MAGeT brain performs
  better than the average multi-atlas approach with the same number of atlases.
  using ANIMAL, 5 or more atlases needed before boost seen. 
\item  more atlases -> smaller template library required to improve on average multi-atlas performance
\item  discuss variance?  best/worst case? --how often do we expect random template library selection to work decently
\end{itemize}

\todo{show cost (in registrations) / benefit tradec off graph:  show number of
registrations per Kappa?  or hours of manual labour per Kappa?)}

%%%%%
%%%%%                  Results: ADNI-1 Screening Validation               %%%%%
%%%%%
\subsection{ADNI-1 Screen Validation}

Ideas: 
\begin{itemize}
\item  A2A shows that if atlas population strongly(?) represents subject set
variability, then free choice from atlas population will produce improvements
(we know this b/c of extensive validation trials). 
\item  what about in the case where atlas population doesn???t strongly
represent subject set variability (e.g. a priori atlas set)?  then, we can use
atlas selection to refine atlas set? 
\end{itemize}

\todo{Kappa against our manual rater is low... explain that}

@@

# recode VISCODE
viscode_levels = list("bl"=1,"bl"=2, "m06"=3,"m12"=4)
yr1$VISCODE <- as.factor(yr1$Visit)
levels(yr1$VISCODE) <-viscode_levels

@@

attach(combined)
vols = data.frame(RID = RID, VISCODE = VISCODE, DX = DX.bl,
                  MAGeT = MAGeT_L + MAGeT_R, 
                  MAPER = MAPER_L + MAPER_R, 
                  SNT   = SNT_L + SNT_R, 
                  UCSD  = UCSD_L + UCSD_R,
                  FS    = FS_L + FS_R, 
                  FSL   = FSL_L + FSL_R)
@

\begin{figure}[h]
<<ADNI-baseline-volumes-boxplot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-prep',cache=T>>=
totals = vols
qplot(DX,value,data=melt(totals,measure.vars=c("FS", "FSL","UCSD", "MAPER","MAGeT","SNT"),na.rm=T),
      colour=variable,geom="boxplot") + 
        xlab("Diagnosis") + ylab("Total Hippocampal Volume (mm3)")

@@

%%%%%
%%%%%             Results: First Episode Patient Validation          %%%%%
%%%%%
\subsection{First Episode Schizophrenic Patients}
High volume correlation between Winterburn segmentation volumes and ground
truth.  (High-ish?) Kappa when using manual segmentations as Atlases.

@@

@
  \caption{{\bf First Episode Schizophrenic Patients.} Comparison of total
  HC volumes for MAGeT against manually rated Hippocampal volumes}
  \label{SZ_volumes}
\end{figure}

%%%%%
%%%%%              Experiments: Winterburn Atlases Validation              %%%%%
%%%%%
\subsection{Winterburn Atlases Validation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                Discussion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               Conclusion 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

\bibliographystyle{plain}
\bibliography{references}
\end{document}
